---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

# eiastats: An R package for accessing data from the U.S. Energy Information Administration

An R package for searching and downloading datasets from the United States'
Energy Information Administration (EIA) API.


## Installation

You can install the released version of eiastats from [CRAN](https://CRAN.R-project.org) with:

```{r eval=FALSE}
install.packages("eiastats")
```
or the latest development version from github with:

```{r, eval = FALSE}
remotes::install_github("mitcda/eiastats")
```

## How to use eaistats

To learn more about the eiastats package, start with the vignettes:
```{r, eval = FALSE}
browseVignettes(package = "eaistats")
```


## Introduction

This package provides functions to search and download data from the United
States' Energy Information Administration's (EIA) API (see
http://www.eia.gov/beta/api/).  There are currently over a million unique time
series available through the API.  To use the package you'll need a *free* API
key from here: http://www.eia.gov/beta/api/register.cfm.

This package extends on the functions in the
[https://cran.r-project.org/web/packages/EIAdata/index.html](EIAdata)
package.^[The functionality in this package broadly mirrors the functionality
available in the
[https://cran.r-project.org/web/packages/wbstats/index.html](wbstats) package
and the author's
[https://cran.r-project.org/web/packages/raustats/index.html](raustats)
package.]  Details of the EIA API are available at:
https://www.eia.gov/opendata/commands.php.

The package has four EIA catalogue-search/information type functions:
  * `eia_search`
  * `eia_bulk_browse`
  * `eia_bulk_search`
  * `eia_category_query`

and four EIA data query functions, that return selected EIA datasets:
  * `eia_series_query`
  * `eia_relation_query`
  * `eia_geoset_query`, and
  * `eia_bulk_stats`.


## Examples

<!--
ABS catalogue statistics may be downloaded, by catalogue number, using the
`abs_cat_stats()` function. The following example downloads all Consumer Price Index
(CPI) data series (ABS Catalogue no. 6401.0).

-->

```{r eval=FALSE}
cpi_all <- abs_cat_stats("6401.0")
```
<!--
To download only the latest statistics reported in Table 1 (ABS groups Tables 1 and
2), simply provide a regular expression to the `tables` argument:
-->

```{r eval=FALSE}
cpi <- abs_cat_stats("6401.0", tables="Table.+1")
```
<!--
The package also provides functions to ABS statistics via the
[ABS.Stat](http://stat.data.abs.gov.au/) Beta API. See the package help and
vignettes for examples. 

-->
